---
title: "polarity.exploration"
output: html_document
---

```{r}
library(malecns)
library(coconatfly)
library(fafbseg)
library(neuprintr)

library(dplyr)
library(tidyr)
library(ggplot2)
library(plotly)
library(stringr)
library(igraph)
library(tidygraph)
library(ggraph)
library(jsonlite)
library(ggplot2)
library(reshape2)
library(Matrix)
library(patchwork)
library(plotly)
```



# 1 Load data

## 1.1 Load male boday annotations
```{r}
synapse_threshold=5
mba<-mcns_body_annotations()
mba.static<-mcns_body_annotations()
mba<-mba%>%mutate(type=ifelse(type=='',NA,type))

```
## 1.2 Get neuprint connection
```{r}
conna = neuprint_login(dataset='male-cns:v0.8',server='https://neuprint-cns.janelia.org/')
mcns.rois = neuprint_ROIs(dataset = 'male-cns:v0.8')
```


# 2 Analyze polarity
## 2.1 Interneurons
### 2.1.1 IN05B002
#### 2.1.1.1 Fetch IDs
```{r}
IN05B002.ids <- mba%>%filter(type=='IN05B002')%>%pull(bodyid)
IN05B002.synapses <- list(neuprint_get_synapses(IN05B002.ids[[1]],roi='VNC'),
                       neuprint_get_synapses(IN05B002.ids[[2]],roi='VNC'))
IN05B002.synapses[[1]]$prepost<- as.factor(IN05B002.synapses[[1]]$prepost)
IN05B002.synapses[[2]]$prepost<- as.factor(IN05B002.synapses[[2]]$prepost)

IN05B002.synapses.all <- neuprint_get_synapses(IN05B002.ids)%>%mutate(prepost=ifelse(prepost==1,'input','output'))
mcell.ids <- mba %>% 
    filter(str_detect(receptor_type, "ppk23")) %>%
    pull(bodyid)
mcell.legbristle.ids <- mba %>% 
    filter(str_detect(receptor_type, "ppk23"),subclass=='leg bristle') %>%
    pull(bodyid)
IN05B002.synapses.all<-IN05B002.synapses.all%>%mutate(prepost=if_else((prepost=='input')&(partner %in% mcell.ids),'m-input',prepost))


fcell.ids <- mba %>% 
    filter(str_detect(receptor_type, "ppk25")) %>%
    pull(bodyid)
fcell.legbristle.ids <- mba %>% 
    filter(str_detect(receptor_type, "ppk25"),subclass=='leg bristle') %>%
    pull(bodyid)
IN05B002.synapses.all<-IN05B002.synapses.all%>%mutate(prepost=if_else((prepost=='input')&(partner %in% fcell.ids),'f-input',prepost))

```
#### 2.1.1.2 Kmeans clustering
```{r}
set.seed(42)  # for reproducibility
IN05B002.synapses[[1]]$cluster <- kmeans(IN05B002.synapses[[1]]%>%select(x,y,z), centers = 6, nstart = 25)$cluster
IN05B002.synapses[[2]]$cluster <- kmeans(IN05B002.synapses[[2]]%>%select(x,y,z), centers = 6, nstart = 25)$cluster

```
#### 2.1.1.3 Viz
```{r}
p1 <- ggplot(IN05B002.synapses[[1]], aes(x = x, y = z, color = prepost)) +
  geom_point(size = 1, alpha = 0.01) +
  scale_color_manual(values = c('1' = "blue", '0' = "red")) +
  scale_y_reverse() +
  coord_fixed() +
  ggtitle(paste(mba %>% filter(bodyid == IN05B002.ids[1]) %>% pull(type), ": ", IN05B002.ids[1])) +
  theme_minimal()

# Second plot
p2 <- ggplot(IN05B002.synapses[[2]], aes(x = x, y = z, color = prepost)) +
  geom_point(size = 1, alpha = 0.01) +
  scale_color_manual(values = c('1' = "blue", '0' = "red")) +
  scale_y_reverse() +
  coord_fixed() +
  ggtitle(paste(mba %>% filter(bodyid == IN05B002.ids[2]) %>% pull(type), ": ", IN05B002.ids[2])) +
  theme_minimal()

# Combine the two plots side by side
p1 + p2
```
#### 2.1.1.4 3D-Viz
```{r}

plot_ly(
  data = IN05B002.synapses.all,
  x = ~x,
  y = ~z,
  z = ~-y,
  color = ~prepost,
  colors = c("yellow","red","green", "blue"),
  type = "scatter3d",
  mode = "markers",
  marker = list(size = 1)
)%>%
  layout(
    scene = list(
      aspectmode = "data"  # ensures equal scaling across x, y, z
    )
  )
```

#### 2.1.1.5 Asymetry M/F input
```{r}
print(IN05B002.synapses.all%>%group_by(prepost)%>%summarize(weight=n()))
```

### 2.1.2 IN05B011
#### 2.1.2.1 Fetch IDs
```{r}
IN05B011.ids <- mba%>%filter(type=='IN05B011')%>%pull(bodyid)
IN05B011.synapses <- list(neuprint_get_synapses(IN05B011.ids[[1]]),
                       neuprint_get_synapses(IN05B011.ids[[2]]),
                       neuprint_get_synapses(IN05B011.ids[[3]]),
                       neuprint_get_synapses(IN05B011.ids[[4]]))
IN05B011.synapses[[1]]$prepost<- as.factor(IN05B011.synapses[[1]]$prepost)
IN05B011.synapses[[2]]$prepost<- as.factor(IN05B011.synapses[[2]]$prepost)
IN05B011.synapses[[3]]$prepost<- as.factor(IN05B011.synapses[[3]]$prepost)
IN05B011.synapses[[4]]$prepost<- as.factor(IN05B011.synapses[[4]]$prepost)
IN05B011.synapses.all <- neuprint_get_synapses(IN05B011.ids)%>%mutate(prepost=ifelse(prepost==1,'input','output'))
mcell.ids <- mba %>% 
    filter(str_detect(receptor_type, "ppk23")) %>%
    pull(bodyid)
IN05B011.synapses.all<-IN05B011.synapses.all%>%mutate(prepost=if_else((prepost=='input')&(partner %in% mcell.ids),'m-input',prepost))

fcell.ids <- mba %>% 
    filter(str_detect(receptor_type, "ppk25")) %>%
    pull(bodyid)
IN05B011.synapses.all<-IN05B011.synapses.all%>%mutate(prepost=if_else((prepost=='input')&(partner %in% fcell.ids),'f-input',prepost))

```
#### 2.1.2.2 Kmeans clustering
```{r}
set.seed(42)  # for reproducibility
IN05B011.synapses[[1]]$cluster <- kmeans(IN05B011.synapses[[1]]%>%select(x,y,z), centers = 6, nstart = 25)$cluster
IN05B011.synapses[[2]]$cluster <- kmeans(IN05B011.synapses[[2]]%>%select(x,y,z), centers = 6, nstart = 25)$cluster
IN05B011.synapses[[3]]$cluster <- kmeans(IN05B011.synapses[[3]]%>%select(x,y,z), centers = 6, nstart = 25)$cluster
IN05B011.synapses[[4]]$cluster <- kmeans(IN05B011.synapses[[4]]%>%select(x,y,z), centers = 6, nstart = 25)$cluster
```
#### 2.1.2.3 Viz
```{r}
p1.xz <- ggplot(IN05B011.synapses[[4]], aes(x = x, y = y, color = prepost)) +
  geom_point(size = 0.1, alpha = 0.5) +
  scale_color_manual(values = c('1' = "blue", '0' = "red")) +
  scale_y_reverse() +
  coord_fixed() +
  ggtitle(paste(mba %>% filter(bodyid == IN05B011.ids[4]) %>% pull(type), ": ", IN05B011.ids[4])) +
  theme_minimal()
p1.xy <- ggplot(IN05B011.synapses[[4]], aes(x = x, y = z, color = prepost)) +
  geom_point(size = 0.1, alpha = 0.5) +
  scale_color_manual(values = c('1' = "blue", '0' = "red")) +
  scale_y_reverse() +
  coord_fixed() +
  ggtitle(paste(mba %>% filter(bodyid == IN05B011.ids[4]) %>% pull(type), ": ", IN05B011.ids[4])) +
  theme_minimal()

# Second plot
p2.xz <- ggplot(IN05B011.synapses[[2]], aes(x = x, y = y, color = prepost)) +
  geom_point(size = 0.1, alpha = 0.5) +
  scale_color_manual(values = c('1' = "blue", '0' = "red")) +
  scale_y_reverse() +
  coord_fixed() +
  ggtitle(paste(mba %>% filter(bodyid == IN05B011.ids[2]) %>% pull(type), ": ", IN05B011.ids[2])) +
  theme_minimal()

p2.xy <- ggplot(IN05B011.synapses[[2]], aes(x = x, y = z, color = prepost)) +
  geom_point(size = 0.1, alpha = 0.5) +
  scale_color_manual(values = c('1' = "blue", '0' = "red")) +
  scale_y_reverse() +
  coord_fixed() +
  ggtitle(paste(mba %>% filter(bodyid == IN05B011.ids[2]) %>% pull(type), ": ", IN05B011.ids[2])) +
  theme_minimal()
# Combine the two plots side by side
(p1.xy+p2.xy)/(p1.xz+p2.xz)
```
#### 2.1.2.4 3D-Viz
```{r}

plot_ly(
  data = IN05B011.synapses.all,
  x = ~x,
  y = ~z,
  z = ~-y,
  color = ~prepost,
  colors = c("yellow","red","green", "blue"),
  type = "scatter3d",
  mode = "markers",
  marker = list(size = 1)
)%>%
  layout(
    scene = list(
      aspectmode = "data"  # ensures equal scaling across x, y, z
    )
  )
```
#### 2.1.1.5 Asymetry M/F input
```{r}
print(IN05B011.synapses.all%>%group_by(prepost)%>%summarize(weight=n(),weight.normed=n()/length(IN05B011.ids)))
```
## 2.2 Ascending Neurns

### 2.2.1 vAB3

#### 2.2.1.1 Fetch IDs
```{r}
AN09B017.ids <- mba%>%filter(type=='AN09B017')%>%pull(bodyid)
AN09B017.synapses <- list(neuprint_get_synapses(AN09B017.ids[[1]]),
                       neuprint_get_synapses(AN09B017.ids[[2]]),
                       neuprint_get_synapses(AN09B017.ids[[3]]),
                       neuprint_get_synapses(AN09B017.ids[[4]]))
AN09B017.synapses[[1]]$prepost<- as.factor(AN09B017.synapses[[1]]$prepost)
AN09B017.synapses[[2]]$prepost<- as.factor(AN09B017.synapses[[2]]$prepost)
AN09B017.synapses[[3]]$prepost<- as.factor(AN09B017.synapses[[3]]$prepost)
AN09B017.synapses[[4]]$prepost<- as.factor(AN09B017.synapses[[4]]$prepost)
AN09B017.synapses.all <- neuprint_get_synapses(AN09B017.ids)%>%mutate(prepost=ifelse(prepost==1,'input','output'))
mcell.ids <- mba %>% 
    filter(str_detect(receptor_type, "ppk23")) %>%
    pull(bodyid)
AN09B017.synapses.all<-AN09B017.synapses.all%>%mutate(prepost=if_else((prepost=='input')&(partner %in% mcell.ids),'m-input',prepost))

fcell.ids <- mba %>% 
    filter(str_detect(receptor_type, "ppk25")) %>%
    pull(bodyid)
AN09B017.synapses.all<-AN09B017.synapses.all%>%mutate(prepost=if_else((prepost=='input')&(partner %in% fcell.ids),'f-input',prepost))

```
#### 2.2.1.2 Kmeans clustering
```{r}
set.seed(42)  # for reproducibility
AN09B017.synapses[[1]]$cluster <- kmeans(AN09B017.synapses[[1]]%>%select(x,y,z), centers = 6, nstart = 25)$cluster
AN09B017.synapses[[2]]$cluster <- kmeans(AN09B017.synapses[[2]]%>%select(x,y,z), centers = 6, nstart = 25)$cluster
AN09B017.synapses[[3]]$cluster <- kmeans(AN09B017.synapses[[3]]%>%select(x,y,z), centers = 6, nstart = 25)$cluster
AN09B017.synapses[[4]]$cluster <- kmeans(AN09B017.synapses[[4]]%>%select(x,y,z), centers = 6, nstart = 25)$cluster
```
#### 2.2.1.3 Viz
```{r}
p1.xz <- ggplot(AN09B017.synapses[[4]], aes(x = x, y = y, color = prepost)) +
  geom_point(size = 0.1, alpha = 0.5) +
  scale_color_manual(values = c('1' = "blue", '0' = "red")) +
  scale_y_reverse() +
  coord_fixed() +
  ggtitle(paste(mba %>% filter(bodyid == AN09B017.ids[4]) %>% pull(type), ": ", AN09B017.ids[4])) +
  theme_minimal()
p1.xy <- ggplot(AN09B017.synapses[[4]], aes(x = x, y = z, color = prepost)) +
  geom_point(size = 0.1, alpha = 0.5) +
  scale_color_manual(values = c('1' = "blue", '0' = "red")) +
  scale_y_reverse() +
  coord_fixed() +
  ggtitle(paste(mba %>% filter(bodyid == AN09B017.ids[4]) %>% pull(type), ": ", AN09B017.ids[4])) +
  theme_minimal()

# Second plot
p2.xz <- ggplot(AN09B017.synapses[[2]], aes(x = x, y = y, color = prepost)) +
  geom_point(size = 0.1, alpha = 0.5) +
  scale_color_manual(values = c('1' = "blue", '0' = "red")) +
  scale_y_reverse() +
  coord_fixed() +
  ggtitle(paste(mba %>% filter(bodyid == AN09B017.ids[2]) %>% pull(type), ": ", AN09B017.ids[2])) +
  theme_minimal()

p2.xy <- ggplot(AN09B017.synapses[[2]], aes(x = x, y = z, color = prepost)) +
  geom_point(size = 0.1, alpha = 0.5) +
  scale_color_manual(values = c('1' = "blue", '0' = "red")) +
  scale_y_reverse() +
  coord_fixed() +
  ggtitle(paste(mba %>% filter(bodyid == AN09B017.ids[2]) %>% pull(type), ": ", AN09B017.ids[2])) +
  theme_minimal()
# Combine the two plots side by side
(p1.xy+p2.xy)/(p1.xz+p2.xz)
```
#### 2.2.1.4 3D-Viz
```{r}

plot_ly(
  data = AN09B017.synapses.all,
  x = ~x,
  y = ~z,
  z = ~-y,
  color = ~prepost,
  colors = c("yellow","red","green", "blue"),
  type = "scatter3d",
  mode = "markers",
  marker = list(size = 1)
)%>%
  layout(
    scene = list(
      aspectmode = "data"  # ensures equal scaling across x, y, z
    )
  )
```
#### 2.2.1.5 Asymetry M/F input
```{r}
print(AN09B017.synapses.all%>%group_by(prepost)%>%summarize(weight=n(),weight.normed=n()/length(AN09B017.ids)))
```

### 2.2.2 PPN1

#### 2.2.2.1 Fetch IDs
```{r}
AN05B102.ids <- mba%>%filter(type=='AN05B102')%>%pull(bodyid)
AN05B102.synapses <- list(neuprint_get_synapses(AN05B102.ids[[1]]),
                       neuprint_get_synapses(AN05B102.ids[[2]]),
                       neuprint_get_synapses(AN05B102.ids[[3]]),
                       neuprint_get_synapses(AN05B102.ids[[4]]))
AN05B102.synapses[[1]]$prepost<- as.factor(AN05B102.synapses[[1]]$prepost)
AN05B102.synapses[[2]]$prepost<- as.factor(AN05B102.synapses[[2]]$prepost)
AN05B102.synapses[[3]]$prepost<- as.factor(AN05B102.synapses[[3]]$prepost)
AN05B102.synapses[[4]]$prepost<- as.factor(AN05B102.synapses[[4]]$prepost)
AN05B102.synapses.all <- neuprint_get_synapses(AN05B102.ids)%>%mutate(prepost=ifelse(prepost==1,'input','output'))
mcell.ids <- mba %>% 
    filter(str_detect(receptor_type, "ppk23")) %>%
    pull(bodyid)
AN05B102.synapses.all<-AN05B102.synapses.all%>%mutate(prepost=if_else((prepost=='input')&(partner %in% mcell.ids),'m-input',prepost))

fcell.ids <- mba %>% 
    filter(str_detect(receptor_type, "ppk25")) %>%
    pull(bodyid)
AN05B102.synapses.all<-AN05B102.synapses.all%>%mutate(prepost=if_else((prepost=='input')&(partner %in% fcell.ids),'f-input',prepost))

```
#### 2.2.2.2 Kmeans clustering
```{r}
set.seed(42)  # for reproducibility
AN05B102.synapses[[1]]$cluster <- kmeans(AN05B102.synapses[[1]]%>%select(x,y,z), centers = 6, nstart = 25)$cluster
AN05B102.synapses[[2]]$cluster <- kmeans(AN05B102.synapses[[2]]%>%select(x,y,z), centers = 6, nstart = 25)$cluster
AN05B102.synapses[[3]]$cluster <- kmeans(AN05B102.synapses[[3]]%>%select(x,y,z), centers = 6, nstart = 25)$cluster
AN05B102.synapses[[4]]$cluster <- kmeans(AN05B102.synapses[[4]]%>%select(x,y,z), centers = 6, nstart = 25)$cluster
```
#### 2.2.2.3 Viz
```{r}
p1.xz <- ggplot(AN05B102.synapses[[4]], aes(x = x, y = y, color = prepost)) +
  geom_point(size = 0.1, alpha = 0.5) +
  scale_color_manual(values = c('1' = "blue", '0' = "red")) +
  scale_y_reverse() +
  coord_fixed() +
  ggtitle(paste(mba %>% filter(bodyid == AN05B102.ids[4]) %>% pull(type), ": ", AN05B102.ids[4])) +
  theme_minimal()
p1.xy <- ggplot(AN05B102.synapses[[4]], aes(x = x, y = z, color = prepost)) +
  geom_point(size = 0.1, alpha = 0.5) +
  scale_color_manual(values = c('1' = "blue", '0' = "red")) +
  scale_y_reverse() +
  coord_fixed() +
  ggtitle(paste(mba %>% filter(bodyid == AN05B102.ids[4]) %>% pull(type), ": ", AN05B102.ids[4])) +
  theme_minimal()

# Second plot
p2.xz <- ggplot(AN05B102.synapses[[2]], aes(x = x, y = y, color = prepost)) +
  geom_point(size = 0.1, alpha = 0.5) +
  scale_color_manual(values = c('1' = "blue", '0' = "red")) +
  scale_y_reverse() +
  coord_fixed() +
  ggtitle(paste(mba %>% filter(bodyid == AN05B102.ids[2]) %>% pull(type), ": ", AN05B102.ids[2])) +
  theme_minimal()

p2.xy <- ggplot(AN05B102.synapses[[2]], aes(x = x, y = z, color = prepost)) +
  geom_point(size = 0.1, alpha = 0.5) +
  scale_color_manual(values = c('1' = "blue", '0' = "red")) +
  scale_y_reverse() +
  coord_fixed() +
  ggtitle(paste(mba %>% filter(bodyid == AN05B102.ids[2]) %>% pull(type), ": ", AN05B102.ids[2])) +
  theme_minimal()
# Combine the two plots side by side
(p1.xy+p2.xy)/(p1.xz+p2.xz)
```
#### 2.2.2.4 3D-Viz
```{r}

plot_ly(
  data = AN05B102.synapses.all,
  x = ~x,
  y = ~z,
  z = ~-y,
  color = ~prepost,
  colors = c("yellow","red","green", "blue"),
  type = "scatter3d",
  mode = "markers",
  marker = list(size = 1)
)%>%
  layout(
    scene = list(
      aspectmode = "data"  # ensures equal scaling across x, y, z
    )
  )
```
#### 2.2.2.4 Asymetry M/F input
```{r}
print(AN05B102.synapses.all%>%group_by(prepost)%>%summarize(weight=n(),weight.normed=n()/length(AN05B102.ids)))
```



# 3 Plots

```{r}
mcell.ids <- mba %>% 
    filter(str_detect(receptor_type, "ppk23")) %>%
    pull(bodyid)

mcell.legbristle.ids <- mba %>% 
    filter(str_detect(receptor_type, "ppk23"),subclass=='leg bristle') %>%
    pull(bodyid)
IN05B002.synapses.all<-IN05B002.synapses.all%>%mutate(prepost=if_else((prepost=='input')&(partner %in% mcell.ids),'m-input',prepost))


fcell.ids <- mba %>% 
    filter(str_detect(receptor_type, "ppk25")) %>%
    pull(bodyid)
fcell.legbristle.ids <- mba %>% 
    filter(str_detect(receptor_type, "ppk25"),subclass=='leg bristle') %>%
    pull(bodyid)

cfps.mcell.out <- cf_partner_summary(cf_ids(malecns = mcell.ids),threshold=5,partners='o')%>%
  mutate(type.pre='mcell')%>%
  group_by(type.post)%>%
  summarize(weight=sum(weight),npost=sum(npost))%>%
  rename(weight=weight)%>%
  mutate(normed.weight = weight/npost)%>%
  mutate(type.pre='mcell')
cfps.mcell.bristle.out <- cf_partner_summary(cf_ids(malecns = mcell.legbristle.ids),threshold=5,partners='o')%>%
  mutate(type.pre='mcell')%>%
  group_by(type.post)%>%
  summarize(weight=sum(weight),npost=sum(npost))%>%
  rename(weight=weight)%>%
  mutate(normed.weight = weight/npost)%>%
  mutate(type.pre='mcell')
cfps.fcell.out <- cf_partner_summary(cf_ids(malecns = fcell.ids),threshold=5,partners='o')%>%
  mutate(type.pre='fcell')%>%
  group_by(type.post)%>%
  summarize(weight=sum(weight),npost=sum(npost))%>%
  rename(weight=weight)%>%
  mutate(normed.weight = weight/npost)%>%
  mutate(type.pre='fcell')
cfps.fcell.bristle.out <- cf_partner_summary(cf_ids(malecns = fcell.legbristle.ids),threshold=5,partners='o')%>%
  mutate(type.pre='fcell')%>%
  group_by(type.post)%>%
  summarize(weight=sum(weight),npost=sum(npost))%>%
  rename(weight=weight)%>%
  mutate(normed.weight = weight/npost)%>%
  mutate(type.pre='fcell')
```

```{r}

AN09B017.normed.input <- cf_partner_summary(cf_ids(malecns='AN09B017'),partners = 'i',threshold = 5,normalise = T)%>%
  mutate(weight=as.numeric(sprintf("%.5f", weight)))
AN05B102.normed.input <- cf_partner_summary(cf_ids(malecns='AN05B102'),partners = 'i',threshold = 5,normalise = T)%>%
  mutate(weight=as.numeric(sprintf("%.5f", weight)))


cfps.fused.out <-  rbind(cfps.fcell.out,cfps.mcell.out)%>%
    select(-npost)%>%
    pivot_wider(
        names_from = type.pre,
        values_from = c(weight, normed.weight),
        values_fn = list(weight = mean, normed.weight = mean),  # or other summaries
        values_fill = 0
    )%>%
  filter(!is.na(type.post))%>%
  left_join(AN09B017.normed.input%>%select(type.pre,weight),by=c('type.post'='type.pre'))%>%
  rename(output.2.AN09B017.normed=weight)%>%
  left_join(AN05B102.normed.input%>%select(type.pre,weight),by=c('type.post'='type.pre'))%>%
  rename(output.2.AN05B102.normed=weight)%>%
  mutate(output.2.AN05B102.normed = ifelse(is.na(output.2.AN05B102.normed), 0, output.2.AN05B102.normed),
         output.2.AN09B017.normed = ifelse(is.na(output.2.AN09B017.normed), 0, output.2.AN09B017.normed))

post.nt<-mba%>%filter(type %in% cfps.fused.out$type.post)%>%select(type,consensus_nt)%>%distinct()
cfps.fused.out<-cfps.fused.out%>%left_join(post.nt,by=c('type.post'='type'))
post.all.in <- cf_partner_summary(cf_ids(malecns=mba%>%
                                           filter(type %in% cfps.fused.out$type.post)%>%
                                           pull(bodyid)),
                                  partners = 'i',threshold=5)%>%
  group_by(type.post)%>%
  summarize(weight=sum(weight))

cfps.fused.out.syn.normed <- cfps.fused.out %>%left_join(post.all.in,by='type.post')%>%
  mutate(post.normed.weight_mcell=weight_mcell/weight,
         post.normed.weight_fcell=weight_fcell/weight)

#bristle
cfps.fused.bristle.out <-  rbind(cfps.fcell.bristle.out,cfps.mcell.bristle.out)%>%
    select(-npost)%>%
    pivot_wider(
        names_from = type.pre,
        values_from = c(weight, normed.weight),
        values_fn = list(weight = mean, normed.weight = mean),  # or other summaries
        values_fill = 0
    )%>%
  filter(!is.na(type.post))%>%
  left_join(AN09B017.normed.input%>%select(type.pre,weight),by=c('type.post'='type.pre'))%>%
  rename(output.2.AN09B017.normed=weight)%>%
  left_join(AN05B102.normed.input%>%select(type.pre,weight),by=c('type.post'='type.pre'))%>%
  rename(output.2.AN05B102.normed=weight)%>%
  mutate(output.2.AN05B102.normed = ifelse(is.na(output.2.AN05B102.normed), 0, output.2.AN05B102.normed),
         output.2.AN09B017.normed = ifelse(is.na(output.2.AN09B017.normed), 0, output.2.AN09B017.normed))

britsle.post.nt<-mba%>%filter(type %in% cfps.fused.bristle.out$type.post)%>%select(type,consensus_nt)%>%distinct()
cfps.fused.bristle.out<-cfps.fused.bristle.out%>%
  left_join(britsle.post.nt,by=c('type.post'='type'))


post.all.in.bristle <- cf_partner_summary(cf_ids(malecns=mba%>%
                                           filter(type %in% cfps.fused.bristle.out$type.post)%>%
                                           pull(bodyid)),
                                  partners = 'i',threshold=5)%>%
  group_by(type.post)%>%
  summarize(weight=sum(weight))



cfps.fused.bristle.out.syn.normed <- cfps.fused.bristle.out %>%left_join(post.all.in.bristle,by='type.post')%>%
  mutate(post.normed.weight_mcell=weight_mcell/weight,
         post.normed.weight_fcell=weight_fcell/weight)
```

#plots with size corresponding to coutput to AN05B102
```{r}

#1
p1 <- ggplot(cfps.fused.bristle.out,
             aes(x = weight_fcell, 
                 y = weight_mcell, 
                 label = type.post,
                 color = consensus_nt,
                 size = output.2.AN05B102.normed
                 )) +
  geom_point(alpha = 0.7) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "gray",alpha=0.5) +
  scale_color_manual(
    values = c(
      "acetylcholine" = "#1f77b4",
      "gaba" = "#ff7f0e",
      "glutamate" = "#2ca02c"
    )
  ) +
  scale_size_continuous(range = c(1, 10)) +
  labs(
    title = "Weight bristle.fcell vs. bristle.mcell",
    x = "Weight (fcell)",
    y = "Weight (mcell)"
  ) +
  theme_minimal()

ggplotly(p1, tooltip = c("label", "size", "color"))
p1
#2
p2 <- ggplot(cfps.fused.bristle.out, 
             aes(x = normed.weight_fcell, 
                 y = normed.weight_mcell, 
                 label = type.post,
                 color = consensus_nt,
                 size = output.2.AN05B102.normed)) +
  geom_point(alpha = 0.7) +
  scale_size_continuous(range = c(1, 10)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "gray",alpha=0.5) +
  scale_color_manual(
    values = c(
      "acetylcholine" = "#1f77b4",
      "gaba" = "#ff7f0e",
      "glutamate" = "#2ca02c"
    )
  ) +
  labs(
    title = "Normed weight bristle.fcell vs. bristle.mcell",
    x = "Weight (fcell)",
    y = "Weight (mcell)"
  ) +
  theme_minimal()

ggplotly(p2, tooltip = c("label", "size", "color"))
p2
#5
p5 <- ggplot(cfps.fused.bristle.out.syn.normed, 
             aes(x = post.normed.weight_fcell, 
                 y = post.normed.weight_mcell, 
                 label = type.post,
                 color = consensus_nt,
                 size = output.2.AN05B102.normed)) +
  geom_point(alpha = 0.7) +
  scale_size_continuous(range = c(1, 10)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "gray",alpha=0.5) +
  scale_color_manual(
    values = c(
      "acetylcholine" = "#1f77b4",
      "gaba" = "#ff7f0e",
      "glutamate" = "#2ca02c"
    )
  ) +
  labs(
    title = "Normed by total in syn of post cell weight bristle.fcell vs. bristle.mcell",
    x = "Weight (fcell)",
    y = "Weight (mcell)"
  ) +
  theme_minimal()

ggplotly(p5, tooltip = c("label", "size", "color"))
p5

#3
p3 <- ggplot(cfps.fused.out, 
             aes(x = weight_fcell,
                 y = weight_mcell, 
                 label = type.post,
                 color = consensus_nt,
                 size = output.2.AN05B102.normed)) +
  geom_point(alpha = 0.7) +
  scale_size_continuous(range = c(1, 10)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "gray",alpha=0.5) +
  scale_color_manual(
    values = c(
      "acetylcholine" = "#1f77b4",
      "gaba" = "#ff7f0e",
      "glutamate" = "#2ca02c"
    )
  ) +
  labs(
    title = "Weight fcell vs. mcell",
    x = "Weight (fcell)",
    y = "Weight (mcell)"
  ) +
  theme_minimal()

ggplotly(p3, tooltip = c("label", "size", "color"))
p3
#4
p4 <- ggplot(cfps.fused.out, 
             aes(x = normed.weight_fcell, 
                 y = normed.weight_mcell, 
                 label = type.post,
                 color = consensus_nt,
                 size = output.2.AN05B102.normed)) +
  geom_point(alpha = 0.7) +
  scale_size_continuous(range = c(1, 10)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "gray",alpha=0.5) +
  scale_color_manual(
    values = c(
      "acetylcholine" = "#1f77b4",
      "gaba" = "#ff7f0e",
      "glutamate" = "#2ca02c"
    )
  ) +
  labs(
    title = "Normed weight fcell vs. mcell",
    x = "Weight (fcell)",
    y = "Weight (mcell)"
  ) +
  theme_minimal()

ggplotly(p4, tooltip = c("label", "size", "color"))

p4

#6
p6 <- ggplot(cfps.fused.out.syn.normed, 
             aes(x = post.normed.weight_fcell, 
                 y = post.normed.weight_mcell, 
                 label = type.post,
                 color = consensus_nt,
                 size = output.2.AN05B102.normed)) +
  geom_point(alpha = 0.7) +
  scale_size_continuous(range = c(1, 10)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "gray",alpha=0.5) +
    scale_color_manual(
    values = c(
      "acetylcholine" = "#1f77b4",
      "gaba" = "#ff7f0e",
      "glutamate" = "#2ca02c"
    )
  ) +
  labs(
    title = "Normed by total in syn of post cell weight fcell vs. mcell",
    x = "Weight (fcell)",
    y = "Weight (mcell)"
  ) +
  theme_minimal()

ggplotly(p6, tooltip = c("label", "size", "color"))
p6
```

#plots with size corresponding to coutput to AN09B017
```{r}

#1
p1 <- ggplot(cfps.fused.bristle.out,
             aes(x = weight_fcell, 
                 y = weight_mcell, 
                 label = type.post,
                 color = consensus_nt,
                 size = output.2.AN09B017.normed
                 )) +
  geom_point(alpha = 0.7) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "gray",alpha=0.5) +
  scale_color_manual(
    values = c(
      "acetylcholine" = "#1f77b4",
      "gaba" = "#ff7f0e",
      "glutamate" = "#2ca02c"
    )
  ) +
  scale_size_continuous(range = c(1, 10)) +
  labs(
    title = "Weight bristle.fcell vs. bristle.mcell",
    x = "Weight (fcell)",
    y = "Weight (mcell)"
  ) +
  theme_minimal()

ggplotly(p1, tooltip = c("label", "size", "color"))
p1

#2
p2 <- ggplot(cfps.fused.bristle.out, 
             aes(x = normed.weight_fcell, 
                 y = normed.weight_mcell, 
                 label = type.post,
                 color = consensus_nt,
                 size = output.2.AN09B017.normed)) +
  geom_point(alpha = 0.7) +
  scale_size_continuous(range = c(1, 10)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "gray",alpha=0.5) +
  scale_color_manual(
    values = c(
      "acetylcholine" = "#1f77b4",
      "gaba" = "#ff7f0e",
      "glutamate" = "#2ca02c"
    )
  ) +
  labs(
    title = "Normed weight bristle.fcell vs. bristle.mcell",
    x = "Weight (fcell)",
    y = "Weight (mcell)"
  ) +
  theme_minimal()

ggplotly(p2, tooltip = c("label", "size", "color"))
p2

#5
p5 <- ggplot(cfps.fused.bristle.out.syn.normed, 
             aes(x = post.normed.weight_fcell, 
                 y = post.normed.weight_mcell, 
                 label = type.post,
                 color = consensus_nt,
                 size = output.2.AN09B017.normed)) +
  geom_point(alpha = 0.7) +
  scale_size_continuous(range = c(1, 10)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "gray",alpha=0.5) +
  scale_color_manual(
    values = c(
      "acetylcholine" = "#1f77b4",
      "gaba" = "#ff7f0e",
      "glutamate" = "#2ca02c"
    )
  ) +
  labs(
    title = "Normed by total in syn of post cell weight bristle.fcell vs. bristle.mcell",
    x = "Weight (fcell)",
    y = "Weight (mcell)"
  ) +
  theme_minimal()

ggplotly(p5, tooltip = c("label", "size", "color"))
p5

#3
p3 <- ggplot(cfps.fused.out, 
             aes(x = weight_fcell,
                 y = weight_mcell, 
                 label = type.post,
                 color = consensus_nt,
                 size = output.2.AN09B017.normed)) +
  geom_point(alpha = 0.7) +
  scale_size_continuous(range = c(1, 10)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "gray",alpha=0.5) +
  scale_color_manual(
    values = c(
      "acetylcholine" = "#1f77b4",
      "gaba" = "#ff7f0e",
      "glutamate" = "#2ca02c"
    )
  ) +
  labs(
    title = "Weight fcell vs. mcell",
    x = "Weight (fcell)",
    y = "Weight (mcell)"
  ) +
  theme_minimal()

ggplotly(p3, tooltip = c("label", "size", "color"))
p3

#4
p4 <- ggplot(cfps.fused.out, 
             aes(x = normed.weight_fcell, 
                 y = normed.weight_mcell, 
                 label = type.post,
                 color = consensus_nt,
                 size = output.2.AN09B017.normed)) +
  geom_point(alpha = 0.7) +
  scale_size_continuous(range = c(1, 10)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "gray",alpha=0.5) +
  scale_color_manual(
    values = c(
      "acetylcholine" = "#1f77b4",
      "gaba" = "#ff7f0e",
      "glutamate" = "#2ca02c"
    )
  ) +
  labs(
    title = "Normed weight fcell vs. mcell",
    x = "Weight (fcell)",
    y = "Weight (mcell)"
  ) +
  theme_minimal()

ggplotly(p4, tooltip = c("label", "size", "color"))

p4

#6
p6 <- ggplot(cfps.fused.out.syn.normed, 
             aes(x = post.normed.weight_fcell, 
                 y = post.normed.weight_mcell, 
                 label = type.post,
                 color = consensus_nt,
                 size = output.2.AN09B017.normed)) +
  geom_point(alpha = 0.7) +
  scale_size_continuous(range = c(1, 10)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "gray",alpha=0.5) +
    scale_color_manual(
    values = c(
      "acetylcholine" = "#1f77b4",
      "gaba" = "#ff7f0e",
      "glutamate" = "#2ca02c"
    )
  ) +
  labs(
    title = "Normed by total in syn of post cell weight fcell vs. mcell",
    x = "Weight (fcell)",
    y = "Weight (mcell)"
  ) +
  theme_minimal()

ggplotly(p6, tooltip = c("label", "size", "color"))
p6
```
### 2.3.4 3D viz F vs M input and connection to secondary
```{r}
library(plotly)

# Define the two Z options
z_vars <- c("post.normed.weight_fcell", "post.normed.weight_mcell")

# Base Z (default)
z0 <- z_vars[1]

# Create plot with fixed X, Y, and initial Z
p <- plot_ly(
  data = cfps.fused.out.syn.normed,
  x = ~output.2.AN09B017.normed,
  y = ~output.2.AN05B102.normed,
  z = ~get(z0),
  color = ~consensus_nt,
  colors = c("blue", "red", "green"),
  type = "scatter3d",
  mode = "markers",
  marker = list(size = 4),
  text = ~paste(
    "Type:", type.post
  ),
  hoverinfo = "text"
)

# Z-axis toggle buttons
z_buttons <- lapply(z_vars, function(v) {
  list(
    method = "restyle",
    args = list("z", list(cfps.fused.out.syn.normed[[v]])),
    label = paste("Z:", v)
  )
})

# Layout with dropdown for Z
p <- layout(p,
  title = "Z-axis Toggle: fcell vs mcell",
  updatemenus = list(
    list(
      buttons = z_buttons,
      direction = "down",
      x = 0.1,
      y = 1.1,
      showactive = TRUE,
      type = "dropdown"
    )
  )
)

p

```


### 2.3.4 3D viz F vs M input and connection to secondary
```{r}
library(plotly)

# Define the two Z options
z_vars <- c("post.normed.weight_fcell", "post.normed.weight_mcell")

# Base Z (default)
z0 <- z_vars[1]

# Create plot with fixed X, Y, and initial Z
p <- plot_ly(
  data = cfps.fused.bristle.out.syn.normed,
  x = ~output.2.AN09B017.normed,
  y = ~output.2.AN05B102.normed,
  z = ~get(z0),
  color = ~consensus_nt,
  colors = c("blue", "red", "green"),
  type = "scatter3d",
  mode = "markers",
  marker = list(size = 4),
  text = ~paste(
    "Type:", type.post
  ),
  hoverinfo = "text"
)

# Z-axis toggle buttons
z_buttons <- lapply(z_vars, function(v) {
  list(
    method = "restyle",
    args = list("z", list(cfps.fused.out.syn.normed[[v]])),
    label = paste("Z:", v)
  )
})

# Layout with dropdown for Z
p <- layout(p,
  title = "Z-axis Toggle: fcell vs mcell",
  updatemenus = list(
    list(
      buttons = z_buttons,
      direction = "down",
      x = 0.1,
      y = 1.1,
      showactive = TRUE,
      type = "dropdown"
    )
  )
)

p

```


#4 Table exploration
```{r}
print(cfps.fused.bristle.out.syn.normed%>%
        group_by(consensus_nt)%>%
        summarize(output.2.AN09B017.normed=sum(output.2.AN09B017.normed),
                  output.2.AN05B102.normed=sum(output.2.AN05B102.normed)))

print(AN09B017.normed.input%>%
        left_join(mba%>%
                    filter(type%in%AN09B017.normed.input$type.pre)%>%
                    select(type,consensus_nt)%>%
                    distinct(),by=c('type.pre'='type'))%>%
        group_by(consensus_nt)%>%
        summarize(output.2.AN09B017.normed=sum(weight)))


print(AN05B102.normed.input%>%
        left_join(mba%>%
                    filter(type%in%AN05B102.normed.input$type.pre)%>%
                    select(type,consensus_nt)%>%
                    distinct(),by=c('type.pre'='type'))%>%
        mutate(post.fm.bristle = type.pre %in% cfps.fused.bristle.out.syn.normed$type.post)%>%
        group_by(consensus_nt,post.fm.bristle)%>%
        summarize(output.2.AN05B102.normed=sum(weight)))


print(AN05B102.normed.input%>%
        left_join(mba%>%
                    filter(type%in%AN05B102.normed.input$type.pre)%>%
                    select(type,consensus_nt)%>%
                    distinct(),by=c('type.pre'='type'))%>%
        mutate(post.fm = type.pre %in% cfps.fused.out.syn.normed$type.post)%>%
        group_by(consensus_nt,post.fm)%>%
        summarize(output.2.AN05B102.normed=sum(weight)))


print(AN09B017.normed.input%>%
        left_join(mba%>%
                    filter(type%in%AN09B017.normed.input$type.pre)%>%
                    select(type,consensus_nt)%>%
                    distinct(),by=c('type.pre'='type'))%>%
        mutate(post.fm.bristle = type.pre %in% cfps.fused.bristle.out.syn.normed$type.post)%>%
        group_by(consensus_nt,post.fm.bristle)%>%
        summarize(output.2.AN09B017.normed=sum(weight)))


print(AN09B017.normed.input%>%
        left_join(mba%>%
                    filter(type%in%AN09B017.normed.input$type.pre)%>%
                    select(type,consensus_nt)%>%
                    distinct(),by=c('type.pre'='type'))%>%
        mutate(post.fm = type.pre %in% cfps.fused.out.syn.normed$type.post)%>%
        group_by(consensus_nt,post.fm)%>%
        summarize(output.2.AN09B017.normed=sum(weight)))

```